---
title: "Test Analysis Notebook"
author: "Your Name"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_notebook:
    toc: true
    toc_float: true
    theme: united
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Set working directory relative to the notebook location
knitr::opts_knit$set(root.dir = normalizePath(".."))
```

# Introduction

This notebook analyzes the dummy data generated for our test analysis.

# Load Required Packages

```{r load-packages}
# Load required packages
library(tidyverse)  # for data manipulation and visualization
library(knitr)      # for nice tables
library(ggplot2)    # for plotting
```

# Load and Inspect Data

```{r load-data}
# Load the dummy data
load("../2_data/1_raw_data/dummy_data.RData")

# Display the first few rows
head(dummy_data) %>%
  kable()

# Basic summary
summary(dummy_data)
```

# Exploratory Data Analysis

## Age Distribution

```{r age-distribution}
# Create histogram of age distribution
ggplot(dummy_data, aes(x = age)) +
  geom_histogram(binwidth = 5, fill = "skyblue", color = "black") +
  labs(title = "Age Distribution",
       x = "Age",
       y = "Count") +
  theme_minimal()

# Age distribution by group
ggplot(dummy_data, aes(x = group, y = age, fill = group)) +
  geom_boxplot() +
  labs(title = "Age Distribution by Group",
       x = "Group",
       y = "Age") +
  theme_minimal()
```

## Score Analysis

```{r score-analysis}
# Score distribution
ggplot(dummy_data, aes(x = score)) +
  geom_density(fill = "lightgreen", alpha = 0.5) +
  labs(title = "Score Distribution",
       x = "Score",
       y = "Density") +
  theme_minimal()

# Score by group and gender
ggplot(dummy_data, aes(x = group, y = score, fill = gender)) +
  geom_boxplot() +
  labs(title = "Score Distribution by Group and Gender",
       x = "Group",
       y = "Score") +
  theme_minimal()
```

# Statistical Analysis

## Group Comparisons

```{r group-comparison}
# T-test comparing scores between groups
t_test_result <- t.test(score ~ group, data = dummy_data)
print(t_test_result)

# ANOVA including gender
model <- aov(score ~ group * gender, data = dummy_data)
summary(model)
```

## Age Group Analysis

```{r age-group-analysis}
# Mean scores by age group
dummy_data %>%
  group_by(age_group) %>%
  summarise(
    mean_score = mean(score),
    sd_score = sd(score),
    n = n()
  ) %>%
  kable()

# Visualize scores across age groups
ggplot(dummy_data, aes(x = age_group, y = score, fill = age_group)) +
  geom_boxplot() +
  labs(title = "Score Distribution by Age Group",
       x = "Age Group",
       y = "Score") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# Conclusions

This analysis has explored the relationships between scores, age groups, gender, and treatment groups in our dummy dataset. Key findings include:

- Distribution of scores across different groups
- Age-related patterns
- Gender differences
- Treatment effects

# Session Info

```{r session-info}
sessionInfo()
``` 